---
title: "FedScore-Survival Demo (heterogeneous data)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

#### Load required packages and source files

```{r}
set.seed(42)

library(tidyverse)
library(doParallel)
library(foreach)
library(dplyr)
library(survival)
library(data.table)
library(pda)
library(AutoScore)
library(survAUC)
library(ggplot2)
library(rstudioapi)

setwd(dirname(getSourceEditorContext()$path))
source("../../code/R/helpers_survival.R")
source("../../code/R/fedscore_survival.R")
```

#### Load demo dataset of 2 sites

```{r}
split_all_site <- readRDS("../../data/survival/demo_hete.rds")
n_site <- length(split_all_site)
names_all_site <- paste0("hete_S", 1:n_site)

for (i in 1:n_site) {
  tmp_dat <- split_all_site[[i]]
  assign(paste0("dat", i, "_split"), tmp_dat)
}
```

#### The sample data has a total of 21 predictors
```{r}
colnames(split_all_site[[1]]$test)
```

#### Generate local variable rankings

```{r}
subfolder_name <- "../../output/survival/rank_hete"
if (!file.exists(subfolder_name)) {
  dir.create(subfolder_name)
  cat(paste("Subfolder '", subfolder_name, "' created successfully.\n", sep = ""))
} else {
  cat(paste("Subfolder '", subfolder_name, "' already exists.\n", sep = ""))
}

rank_all_site <- paste0("rank.s", 1:n_site)
n_cores <- detectCores() - 1
cl <- makeCluster(n_cores)
registerDoParallel(cl)
foreach (i = 1:n_site) %dopar% {
  library(tidyverse)
  rank_all_site <- paste0("rank.s", 1:n_site)
  tmp_dat_all <- readRDS("../../data/survival/demo_hete.rds")
  tmp_dat <- tmp_dat_all[[i]]
  tmp_rank <- AutoScore::AutoScore_rank_Survival(tmp_dat$all_train)
  assign(rank_all_site[i], tmp_rank)
  tmp_file <- paste0("../../output/survival/rank_hete/rank", i, ".csv")
  write_rank(tmp_rank, tmp_file)
}
stopCluster(cl)
```

#### Read local variable rankings and calculate federated ranking

```{r}
rank_all_site <- paste0("rank.s", 1:n_site)
for (i in 1:n_site) {
  tmp_rank <- read.csv(paste0("../../output/survival/rank_hete/rank", i, ".csv"))
  assign(rank_all_site[i], tmp_rank$var)
}

weight <- c()
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  weight <- c(weight, nrow(tmp_dat$all_train))
}
weight <- weight/sum(weight)
rank.fed <- AutoScore_Frank(weight = weight, K = n_site, path = "../../output/survival/rank_hete/")
var.rank <- rank.fed$var

saveRDS(var.rank, "../../output/survival/rank/fed_rank_hete.rds")
var.rank <- readRDS("../../output/survival/rank/fed_rank_hete.rds")
```

#### Calculate local and federated cutoff vectors for numerical variables

```{r}
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  write_cutoff(df = tmp_dat$all_train, sitename = names_all_site[i], path = "../../output/survival/cutoff_hete.json",
               quantiles = c(0, 0.2, 0.4, 0.6, 0.8, 1))
}
all_cutoff <- read_all_cutoff(names_all_site, path = "../../output/survival/cutoff_hete.json")

uni_cut <- get_uni_cut(names_all_site, path = "../../output/survival/cutoff_hete.json", weight = weight)
order_uni_cut <- get_ordered_cut(var.rank, uni_cut)
saveRDS(uni_cut, "../../output/survival/uni_cut_hete.rds")
uni_cut <- readRDS("../../output/survival/uni_cut_hete.rds")
```

#### Run federated Cox regression with five fold CV

```{r}
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  write_Lbeta(names_all_site[i], tmp_dat$train, var.rank, uni_cut, fold = 5)
}

for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  write_Ds(names_all_site[i], names_all_site, tmp_dat$train, var.rank, uni_cut, heterogeneity = T, fold = 5)
}

for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  write_surr(tmp_dat$train, names_all_site[i], names_all_site, var.rank, heterogeneity = "hete", uni_cut, fold = 5)
}

subfolder_name <- "../../output/survival/fedsurv_hete"
if (!file.exists(subfolder_name)) {
  dir.create(subfolder_name)
  cat(paste("Subfolder '", subfolder_name, "' created successfully.\n", sep = ""))
} else {
  cat(paste("Subfolder '", subfolder_name, "' already exists.\n", sep = ""))
}

get_federatedCox(data_train_all = dat1_split$train,
                 site_list = names_all_site,
                 var_list = var.rank,
                 heterogeneity = "hete",
                 uni_cut = uni_cut,
                 fold = 5,
                 csv_name = "../../output/survival/fedsurv_hete/coef_global_hete_trainCV5")
```

#### Caculate AUROC values and generate parsimony plots

```{r}
auc_df <- data.frame(matrix(nrow = 0, ncol = 4))
colnames(auc_df) <- c("AUC", "Site", "Model", "fold")
nmodel <- ncol(dat1_split$test) - 2
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  tmp_df <- Get_auc_bySite(tmp_dat$train, nsite = i, var.rank, uni_cut, nmodel, nfold = 5, heterogeneity = T)
  auc_df <- rbind(auc_df, tmp_df)
}
tmp_df_avg <- auc_df %>% group_by(Model, fold) %>% 
  summarize(AUC = mean(AUC), .groups = "drop") %>% 
  arrange(Model, fold) %>% 
  mutate(Site = "Site0")

parsimony_plot_by_site(tmp_df_avg, site_name = "Site0", output_path = "../../output/survival/fedsurv_hete/rawPara_fed_plot_all.pdf", nfold = 5)
```

#### Final fit

1. Select final variables (e.g. the first 6 variables) & Change reference
2. Fit final federated Cox regression
3. Generate final score table
4. Test final model
5. Extract test results

```{r}
var_max <- 6
var_final <- var.rank[1:var_max]

subfolder_name <- sprintf("../../output/survival/v%d_hete", var_max)
if (!file.exists(subfolder_name)) {
  dir.create(subfolder_name)
  cat(paste("Subfolder '", subfolder_name, "' created successfully.\n", sep = ""))
} else {
  cat(paste("Subfolder '", subfolder_name, "' already exists.\n", sep = ""))
}

  
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  write_Lbeta_final(names_all_site[i], tmp_dat$all_train, var_final, uni_cut, modelIndex = "change_ref")
}
  
ref <- find_bbar("hete", names_all_site, dat1_split$all_train, var_final, uni_cut, modelIndex = "change_ref", heterogeneity = T)
write.csv(data.frame(name = names(ref), v1 = ref), "../../output/survival/ref_hete.csv", row.names = FALSE)
  
ref0 <- read.csv("../../output/survival/ref_hete.csv")
ref <- ref0$v1
names(ref) <- ref0$name
  
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "_split"))
  tmp_dat1 <- change_to_newref(tmp_dat$all_train, var_final, uni_cut, ref)
    assign(paste0("dat", i, "transformed_train_final"), tmp_dat1)
}
  
# -----------------------
# Final fit
# -----------------------
  
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "transformed_train_final"))
  write_Lbeta_final(names_all_site[i], tmp_dat, var_final, uni_cut, modelIndex = "final") 
  }
  
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "transformed_train_final"))
  write_Ds_final(names_all_site[i], names_all_site, tmp_dat, var_final, uni_cut, modelIndex = "final", heterogeneity = T)
  }
  
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "transformed_train_final"))
  write_surr_final(tmp_dat, names_all_site[i], names_all_site, modelIndex = "final", heterogeneity = "hete")
  }
  
get_federatedCox_final(dat1transformed_train_final, names_all_site, var = length(var_final), modelIndex = "final", 
                         heterogeneity = "hete", i_fold="NA", csv_name = "../../output/survival/fedsurv_hete/coef_global_hete_trainCV")
  
# -----------------------
# Score table
# -----------------------
  
time_point <- c(1:29)
  
csv_name <- sprintf("../../output/survival/fedsurv_hete/coef_global_hete_trainCVvar%d_model%s_fold%s.csv", var = length(var_final), "final", "NA")
coef <- read.csv(csv_name)
coef_vec <- coef$V1
names(coef_vec) <- coef$X
  
score_tbl <- show_score_table(dat1transformed_train_final, coef_vec, final_variables = var_final, max_score = 100)
  
# -----------------------
# Testing
# -----------------------
  
for (i in 1:n_site) {
    tmp_dat <- get(paste0("dat", i, "_split"))
    tmp_dat1 <- change_to_newref(tmp_dat$test, var_final, uni_cut, ref)
    assign(paste0("dat", i, "transformed_test_final"), tmp_dat1)
}

sink(sprintf("../../output/survival/v%d_hete/Final_fed_test_max_v%d.txt", var_max, var_max))
for (i in 1:n_site) {
  tmp_dat <- get(paste0("dat", i, "transformed_test_final"))
  print(sprintf("(hete) generating auc for Site%d validation for model fed", i))
  FedScore_survival_testing(tmp_dat, score_tbl, var_final, time_point = time_point)
}
sink()
  
# -----------------------
# Extract
# -----------------------
  
input <- sprintf("../../output/survival/v%d_hete/Final_fed_test_max_v%d.txt", var_max, var_max)
output <- sprintf("../../output/survival/v%d_hete/Final_fed_testAUC_max_v%d.csv", var_max, var_max)
res <- extract_final(input, output)
```
